---
title: "**The Impact of Structure on Software Merging: Semistructured versus Structured Merge**"
output:
  html_document:
    theme: yeti
    toc: true
    toc_float: true
    df_print: paged
---

<style>
  .list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  	z-index: 2;
  	color: #ffffff;
  	background-color: #222;
  	border-color: #222;
  }
  .nav-pills > li.active > a, .nav-pills > li.active > a:hover, .nav-pills > li.active > a:focus {
	  color: #ffffff;
	  background-color: #222;
  }
  a, a:hover, a:focus {
	  color: #222;
  }
</style>

## Abstract {.tabset .tabset-fade .tabset-pills}

Merge conflicts often occur when developers concurrently change the same code artifacts. While state-of-practice unstructured merge tools (e.g git merge) try to automatically resolve merge conflicts via textual similarity, semistructured and structured merge tools try to go further by exploiting the syntactic structure and semantics of the involved artifacts. Although there is evidence that semistructured merge has significant advantages over unstructured merge, and that structured merge reports significantly less conflicts than unstructured merge, it is unknown how semistructured merge compares with structured merge. In an empirical study, we compare semistructured and structured merge by reproducing more than 40,000 merge scenarios from more than 500 projects. We assess how often the tools report different results. We also identify conflicts incorrectly reported by one tool but not by the other (false positives), and conflicts correctly reported by one tool but missed by the other (false negatives). Our results show that the tools differ on 24% of the scenarios with conflicts. Semistructured merge reports more false positives, whereas structured merge has more false negatives. Finally, we observe that adapting a semistructured merge tool to resolve a particular kind of conflict makes semistructured and structured merge even closer.

* [Preprint](https://github.com/delaevernu/delaevernu.github.io/tree/master/svj/preprint.pdf)
* [Replication Package](https://github.com/delaevernu/delaevernu.github.io/tree/master/svj/replication/)


```{r include=FALSE}
library(ggplot2)
library(reshape2)
library(beanplot)
library(xlsx)
library(coin)
library(scales) 
library(knitr)
library(kableExtra)
library(DT)
library(tidyr)
library(effsize)
library(dplyr)

knitr::opts_chunk$set(echo=FALSE)
```

```{r include=FALSE}
#path of the files generated by experiment.jar
importPath = "C:/Users/Guilherme/Desktop/miner-ci/BACKUP_0219/" 

resultFPFNFile	= "numbers-projects.csv"
resultFPFNRaw = read.csv(file=paste(importPath, resultFPFNFile, sep=""), header=TRUE, sep=";")
row.names(resultFPFNRaw) <- NULL


getdata <- function(column1,column2,column3){
	data = data.frame(resultFPFNRaw[column1], resultFPFNRaw[column2], resultFPFNRaw[column3])
	data["Percentual"] <- round((data[column3]/data[column2])*100,2)
	
	withmean <- computeMean(data,column1,column2,column3,"Percentual",data)
	withstdv <- computeStandardDeviation(data,column1,column2,column3,"Percentual",data)
	withtotal<- computeAggregated(data,column1,column2,column3,"Percentual",data)
	
	data <- rbind(data, withmean)
	data <- rbind(data, withstdv)
	data <- rbind(data, withtotal)

	return(data)
}

filterZeroData <- function(df, filteredColumn){
	temp <- filter(df, df[filteredColumn] > 0, projectName != 'MEAN', projectName != 'STANDARD DEVIATION', projectName != 'TOTAL')
	mean = round(mean(temp$Percentual,na.rm=TRUE),2)
	stddvn  = round(sd(temp$Percentual,na.rm = TRUE),2)

	datafiltered <- filter(df, df[filteredColumn] > 0, projectName != 'TOTAL')
	datafiltered[datafiltered$projectName == "MEAN",][,5] = mean
	datafiltered[datafiltered$projectName == "STANDARD DEVIATION",][,5] = stddvn
	return(datafiltered)
}

filterZeroDataFPFN <- function(df){
	temp <- filter(df, scenariosWithCommonChangedMethods > 0, projectName != 'MEAN', projectName != 'STANDARD DEVIATION', projectName != 'TOTAL')
	mean = round(mean(temp$Percentual,na.rm=TRUE),2)
	stddvn  = round(sd(temp$Percentual,na.rm = TRUE),2)
	return(temp)
}

computeMean <- function(df,column1,column2,column3,column4,target) {
	mean    = round(mean(df$Percentual,na.rm=TRUE),2)
	nrow    = data.frame("MEAN", "", "",mean)
	colnames(nrow) <- c(column1,column2,column3,column4)
	return(nrow)

}

computeStandardDeviation <- function(df,column1,column2,column3,column4,target) {
	stddvn  = round(sd(df$Percentual,na.rm = TRUE),2)
	nrow    = data.frame("STANDARD DEVIATION", "", "",stddvn )
	colnames(nrow) <- c(column1,column2,column3,column4)
	return(nrow)
}

computeAggregated <- function(df,column1,column2,column3,column4,target) {
	sum1 	= sum(df[column2])
	sum2 	= sum(df[column3])
	value = 0
	value <- round((sum2/sum1)*100,2)

	nrow  = data.frame("TOTAL", sum1, sum2, value)
	colnames(nrow) <- c(column1,column2,column3,column4)
  return(nrow)
}


getRandString<-function(len=12){
	return(paste(sample(c(rep(0:9,each=5),LETTERS,letters),len,replace=TRUE),collapse=''))
} 

exportDataToExcel <- function(datatoexport,name){
	fileexcel = paste(name,".xlsx")
	fileexcel = paste(exportPath, fileexcel, sep="")
	write.xlsx(format(datatoexport, decimal.mark="."), fileexcel) 
}

drawboxplot <- function(nd, title){
	theme = theme_set(theme_minimal(base_size = 18))
	theme = theme_update(legend.position="right", legend.title=element_blank(), panel.grid.major.x=element_blank())
	theme = theme_update(axis.text.x=element_blank(), axis.ticks.x = element_blank(), axis.line.x = element_blank(), axis.title.x=element_blank())
	theme = theme_update(axis.text.y=element_blank(), axis.ticks.y = element_blank(), axis.line.y = element_blank(), axis.title.y=element_blank())
	theme = theme_update(axis.line.y = element_blank(), axis.title.y=element_blank(), axis.text.y = element_text(colour="grey"), axis.ticks.y= element_line(colour="grey"))
	theme = theme_update(plot.title = element_text(hjust = 0.5))
	
	boxplot = ggplot(nd ,aes(variable, value, color=variable, fill=variable)) + scale_y_continuous(breaks = seq(0, 100, 20))
	#boxplot = boxplot + ggtitle(title) #uncomment to show plot title
	
	boxplot = boxplot + geom_boxplot(outlier.colour="black", outlier.shape=19,outlier.size=1) 
	#boxplot = boxplot + geom_boxplot(outlier.colour="black", outlier.shape=NA,outlier.size=NA) uncomment to hide outliers
	
	boxplot = boxplot + stat_summary(geom = "crossbar", width=1, fatten=0, fun.data = function(x){ return(c(y=median(x), ymin=median(x), ymax=median(x))) })
	
	#mean.n <- function(x){ return(c(y = median(x)*0.97, label = round(mean(x),2))) }
	#boxplot = boxplot + stat_summary(fun.data = mean.n, geom = "text", fun.y = mean, colour = "black")
	
	boxplot = boxplot + scale_fill_manual(values=c("#ffffff", "#ffffff", "#ffffff", "#ffffff" ))

	return(boxplot)
}


drawplots <- function(diffByAllScenarios, diffByConflictingScenarios, diffByconfChanceFiles, diffByconfChanceMethods){
	aux <- head(diffByAllScenarios, -3)
	diffByAllScenariospct  = subset(aux, select = c("Percentual"))
	diffByAllScenariospct  <- setNames(diffByAllScenariospct, c("diffByAllScenarios"))
	
	aux <- head(diffByConflictingScenarios, -3)
	diffByConflictingScenariospct  = subset(aux, select = c("Percentual"))
	diffByConflictingScenariospct  <- setNames(diffByConflictingScenariospct, c("diffByConflictingScenarios"))
	
	aux <- head(diffByconfChanceFiles, -3)
	diffByconfChanceFilespct  = subset(aux, select = c("Percentual"))
	diffByconfChanceFilespct  <- setNames(diffByconfChanceFilespct, c("diffByconfChanceFiles"))
	
	aux <- head(diffByconfChanceMethods, -3)
	diffByconfChanceMethodspct  = subset(aux, select = c("Percentual"))
	diffByconfChanceMethodspct  <- setNames(diffByconfChanceMethodspct, c("diffByconfChanceMethods"))
	
	
	fa <- data.frame(diffByAllScenariospct$diffByAllScenarios
					, diffByConflictingScenariospct$diffByConflictingScenarios
					, diffByconfChanceFilespct$diffByconfChanceFiles
					, diffByconfChanceMethodspct$diffByconfChanceMethods
	)
	

	colnames(fa) <- c("All scenarios", "Conflicting scenarios", "Chance of conflicts in Files", "Chance of conflicts in Methods")
	
	nd <- melt(fa)
	
	drawboxplot(nd, "How often semistructured and \n structured merge differ(%)")
}


conflictingScenariosSsmerge  <- getdata("projectName","numberOfScenarios","scenariosWithSsmergeConfNoWS")
conflictingScenariosJdime <- getdata("projectName","numberOfScenarios","scenariosWithJdimeConf")
conflictingScenarios <- data.frame(conflictingScenariosSsmerge["projectName"]
	,conflictingScenariosSsmerge["numberOfScenarios"]
	,conflictingScenariosSsmerge["scenariosWithSsmergeConfNoWS"]
	,conflictingScenariosJdime["scenariosWithJdimeConf"]
)

#chance of conflicts by file and methods
confChanceFiles <- getdata("projectName","numberOfScenarios","scenariosWithCommonChangedFiles")
confChanceMethods <- getdata("projectName","numberOfScenarios","scenariosWithCommonChangedMethods")

#differences by all scenarios
conflictingScenariosOnlyWithSsmergeConf <- getdata("projectName","numberOfScenarios","scenariosOnlyWithSsmergeConfNoWS")
conflictingScenariosOnlyWithJdimeConf <- getdata("projectName","numberOfScenarios","scenariosOnlyWithJdimeConfNoWS")
diffByAllScenarios <- data.frame(conflictingScenariosOnlyWithSsmergeConf["projectName"]
	,conflictingScenariosOnlyWithSsmergeConf["numberOfScenarios"]
	,conflictingScenariosOnlyWithSsmergeConf["scenariosOnlyWithSsmergeConfNoWS"]
	,conflictingScenariosOnlyWithJdimeConf["scenariosOnlyWithJdimeConfNoWS"]
	,conflictingScenariosOnlyWithSsmergeConf["Percentual"] + conflictingScenariosOnlyWithJdimeConf["Percentual"])#joining differents types of fn
diffByAllScenariosNoZero <- filterZeroData(diffByAllScenarios, "Percentual")


#differences by conflicting scenarios
conflictingScenariosOnlyWithSsmergeConf <- getdata("projectName","conflictingScenarios","scenariosOnlyWithSsmergeConfNoWS")
conflictingScenariosOnlyWithJdimeConf <- getdata("projectName","conflictingScenarios","scenariosOnlyWithJdimeConfNoWS")
diffByConflictingScenarios <- data.frame(conflictingScenariosOnlyWithSsmergeConf["projectName"]
	,conflictingScenariosOnlyWithSsmergeConf["conflictingScenarios"]
	,conflictingScenariosOnlyWithSsmergeConf["scenariosOnlyWithSsmergeConfNoWS"]
	,conflictingScenariosOnlyWithJdimeConf["scenariosOnlyWithJdimeConfNoWS"]
	,conflictingScenariosOnlyWithSsmergeConf["Percentual"] + conflictingScenariosOnlyWithJdimeConf["Percentual"])#joining differents types of fn
diffByConflictingScenariosNoZero <- filterZeroData(diffByConflictingScenarios, "Percentual")

#differences by scenarios with chance of conflict in files
conflictingScenariosOnlyWithSsmergeConf <- getdata("projectName","scenariosWithCommonChangedFiles","scenariosOnlyWithSsmergeConfNoWS")
conflictingScenariosOnlyWithJdimeConf <- getdata("projectName","scenariosWithCommonChangedFiles","scenariosOnlyWithJdimeConfNoWS")
diffByconfChanceFiles <- data.frame(conflictingScenariosOnlyWithSsmergeConf["projectName"]
	,conflictingScenariosOnlyWithSsmergeConf["scenariosWithCommonChangedFiles"]
	,conflictingScenariosOnlyWithSsmergeConf["scenariosOnlyWithSsmergeConfNoWS"]
	,conflictingScenariosOnlyWithJdimeConf["scenariosOnlyWithJdimeConfNoWS"]
	,conflictingScenariosOnlyWithSsmergeConf["Percentual"] + conflictingScenariosOnlyWithJdimeConf["Percentual"])#joining differents types of fn
diffByconfChanceFilesNoZero <- filterZeroData(diffByconfChanceFiles, "Percentual")

#differences by scenarios with chance of conflict in methods
conflictingScenariosOnlyWithSsmergeConf <- getdata("projectName","scenariosWithCommonChangedMethods","scenariosOnlyWithSsmergeConfNoWS")
conflictingScenariosOnlyWithJdimeConf <- getdata("projectName","scenariosWithCommonChangedMethods","scenariosOnlyWithJdimeConfNoWS")
diffByconfChanceMethods <- data.frame(conflictingScenariosOnlyWithSsmergeConf["projectName"]
	,conflictingScenariosOnlyWithSsmergeConf["scenariosWithCommonChangedMethods"]
	,conflictingScenariosOnlyWithSsmergeConf["scenariosOnlyWithSsmergeConfNoWS"]
	,conflictingScenariosOnlyWithJdimeConf["scenariosOnlyWithJdimeConfNoWS"]
	,conflictingScenariosOnlyWithSsmergeConf["Percentual"] + conflictingScenariosOnlyWithJdimeConf["Percentual"])#joining differents types of fn
diffByconfChanceMethodsNoZero <- filterZeroData(diffByconfChanceMethods, "Percentual")

```

## How many conflicts arise from the use of semistructured and structured merge?

```{r}
totalConflicts <- getdata("projectName","ssmergeConfNoWS","jdimeConf")
total_SS = as.numeric(totalConflicts[totalConflicts$projectName == "TOTAL",][,2]) 
total_ST = as.numeric(totalConflicts[totalConflicts$projectName == "TOTAL",][,3])
aFPFN_summary <- data.frame("Semistructured Merge" = c(total_SS), "Structured Merge" = c(total_ST))
```

There is a difference of **`r round(((total_ST - total_SS)/total_SS)*100,2)`%** in the number of reported conflicts.

```{r}
datatable(aFPFN_summary, class = 'cell-border stripe compact stripe', colnames = c('Semistructured Merge','Structured Merge'))
```


Merge scenarios had at least one conflict with _semistructured_ merge on average **`r conflictingScenariosSsmerge[conflictingScenariosSsmerge$projectName == "MEAN",][,4]`%** of the considered merge scenarios, with a standard deviation of **`r conflictingScenariosSsmerge[conflictingScenariosSsmerge$projectName == "STANDARD DEVIATION",][,4]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r conflictingScenariosSsmerge[conflictingScenariosSsmerge$projectName == "TOTAL",][,4]`%**  of the considered merge scenarios. Besides that, merge scenarios had at least one conflict with _structured_ merge on average **`r conflictingScenariosJdime[conflictingScenariosJdime$projectName == "MEAN",][,4]`%** of the considered merge scenarios, with a standard deviation of **`r conflictingScenariosJdime[conflictingScenariosJdime$projectName == "STANDARD DEVIATION",][,4]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r conflictingScenariosJdime[conflictingScenariosJdime$projectName == "TOTAL",][,4]`%**  of the considered merge scenarios.

```{r}
  datatable(conflictingScenarios, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Merge Scenarios', 'Conflicting Semistructured Merge Scenarios','Conflicting Structured Merge Scenarios'))  
```

##
Statistical significance, consider a confidence level of 0.95 (p-value = 0.05):

```{r}
	aux <- head(conflictingScenariosJdime, -3)
	cf_ST  = subset(aux, select = c("Percentual"))
	cf_ST  <- setNames(cf_ST, c("Structured"))
	
	aux <- head(conflictingScenariosSsmerge, -3)
	cf_SS  = subset(aux, select = c("Percentual"))
	cf_SS  <- setNames(cf_SS, c("Semistructured"))
	print(wilcox.test(cf_SS$Semistructured,cf_ST$Structured,paired=TRUE))
```

Strength/magnitude of the statistical claim (_effect size_):
 
```{r}
	print(cliff.delta(cf_SS$Semistructured,cf_ST$Structured,return.dm=TRUE))
```
 
## How often do semistructured and structured merge differ with respect to conflict occurrence? {.tabset .tabset-fade .tabset-pills}
### By All Scenarios

The tools differ on average **`r diffByAllScenarios[diffByAllScenarios$projectName == "MEAN",][,5]`%** of the considered merge scenarios, with a standard deviation of **`r diffByAllScenarios[diffByAllScenarios$projectName == "STANDARD DEVIATION",][,5]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r diffByAllScenarios[diffByAllScenarios$projectName == "TOTAL",][,5]`%**  of the considered merge scenarios.
<!-- (`r diffByAllScenariosNoZero[diffByAllScenariosNoZero$projectName == "MEAN",][,5]` ± `r diffByAllScenariosNoZero[diffByAllScenariosNoZero$projectName == "STANDARD DEVIATION",][,5]`% filtering zero-occurrences)-->

```{r}
  datatable(diffByAllScenarios, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Merge Scenarios', 'Conflicting Merge Scenarios Only With Semistructured Merge','Conflicting Merge Scenarios Only With Structured Merge','%'))  
```

### By Conflicting Scenarios

The tools differ on average **`r diffByConflictingScenarios[diffByConflictingScenarios$projectName == "MEAN",][,5]`%** of the considered merge scenarios, with a standard deviation of **`r diffByConflictingScenarios[diffByConflictingScenarios$projectName == "STANDARD DEVIATION",][,5]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r diffByConflictingScenarios[diffByConflictingScenarios$projectName == "TOTAL",][,5]`%**  of the considered merge scenarios.
<!-- (`r diffByConflictingScenariosNoZero[diffByConflictingScenariosNoZero$projectName == "MEAN",][,5]` ± `r diffByConflictingScenariosNoZero[diffByConflictingScenariosNoZero$projectName == "STANDARD DEVIATION",][,5]`% filtering zero-occurrences)-->


```{r}
  datatable(diffByConflictingScenarios, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Conflicting Merge Scenarios', 'Conflicting Merge Scenarios Only With Semistructured Merge','Conflicting Merge Scenarios Only With Structured Merge','%')) 
```

### When there is chance of conflicts in Files

The tools differ on average **`r diffByconfChanceFiles[diffByconfChanceFiles$projectName == "MEAN",][,5]`%** of the considered merge scenarios, with a standard deviation of **`r diffByconfChanceFiles[diffByconfChanceFiles$projectName == "STANDARD DEVIATION",][,5]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r diffByconfChanceFiles[diffByconfChanceFiles$projectName == "TOTAL",][,5]`%**  of the considered merge scenarios.
<!-- (`r diffByconfChanceFilesNoZero[diffByconfChanceFilesNoZero$projectName == "MEAN",][,5]` ± `r diffByconfChanceFilesNoZero[diffByconfChanceFilesNoZero$projectName == "STANDARD DEVIATION",][,5]`% filtering zero-occurrences)-->


```{r}
  datatable(diffByconfChanceFiles, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Merge Scenarios With Common Changed Files', 'Conflicting Merge Scenarios Only With Semistructured Merge','Conflicting Merge Scenarios Only With Structured Merge','%')) 
```

<!-- ### When there is chance of conflicts in Methods

The tools differ on average **`r diffByconfChanceMethods[diffByconfChanceMethods$projectName == "MEAN",][,5]`%** of the considered merge scenarios, with a standard deviation of **`r diffByconfChanceMethods[diffByconfChanceMethods$projectName == "STANDARD DEVIATION",][,5]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r diffByconfChanceMethods[diffByconfChanceMethods$projectName == "TOTAL",][,5]`%**  of the considered merge scenarios.
<!-- (`r diffByconfChanceMethodsNoZero[diffByconfChanceMethodsNoZero$projectName == "MEAN",][,5]` ± `r diffByconfChanceMethodsNoZero[diffByconfChanceMethodsNoZero$projectName == "STANDARD DEVIATION",][,5]`% filtering zero-occurrences)-->


```{r}
#datatable(diffByconfChanceMethods, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Merge Scenarios With Common Changed Methods', 'Conflicting Merge Scenarios Only With Semistructured Merge','Conflicting Merge Scenarios Only With Structured Merge','%')) 
```


### Boxplot
```{r}
	#diffboxfile <- drawplots(diffByAllScenarios, diffByConflictingScenarios, diffByconfChanceFiles, diffByconfChanceMethods)
	#print(diffboxfile)

	par(mar=c(11,6,1,1))
  boxplot(diffByAllScenarios$Percentual,diffByConflictingScenarios$Percentual, diffByconfChanceFiles$Percentual, names=c("All Scenarios", "Conf. Scenarios","Conf. chance in Files"),las=2, ylab = "(%)")
#boxplot(diffByAllScenarios$Percentual,diffByConflictingScenarios$Percentual, diffByconfChanceFiles$Percentual,diffByconfChanceMethods$Percentual, names=c("All Scenarios", "Conf. Scenarios","Conf. chance in Files", "Conf. chance in Methods"),las=2, ylab = "(%)")
#boxplot(diffByAllScenarios$Percentual,diffByConflictingScenariosNoZero$Percentual, diffByconfChanceFilesNoZero$Percentual,diffByconfChanceMethodsNoZero$Percentual, names=c("All Scenarios", "Conf. Scenarios","Conf. chance in Files", "Conf. chance in Methods"),las=2, ylab = "(%)")
```
 
```{r}
	###############################################################
	#FALSE POSITIVES AND FALSE NEGATIVES ANALYSIS#
	###############################################################

#false positives by all scenarios
fpastscenarios <- getdata("projectName","numberOfScenarios","travisPASSEDssmerge")
fpassscenarios <- getdata("projectName","numberOfScenarios","travisPASSEDjdimeNoCLWS")

#false positives by chance of conflict in methods
fpastscenariosByConfChancMethods <- getdata("projectName","scenariosWithCommonChangedMethods","travisPASSEDssmerge")
fpastscenariosByConfChancMethodsNoZero <- filterZeroDataFPFN(fpastscenariosByConfChancMethods)
fpassscenariosByConfChancMethods <- getdata("projectName","scenariosWithCommonChangedMethods","travisPASSEDjdimeNoCLWS")
fpassscenariosByConfChancMethodsNoZero <- filterZeroDataFPFN(fpassscenariosByConfChancMethods)


#false negatives by all scenarios
fnassscenarios1 <- getdata("projectName","numberOfScenarios","travisFAILEDssmerge")
fnassscenarios2 <- getdata("projectName","numberOfScenarios","travisERROREDssmerge")
fnassscenarios <- data.frame(fnassscenarios1["projectName"]
	,fnassscenarios1["numberOfScenarios"]
	,fnassscenarios2["travisERROREDssmerge"]
	,fnassscenarios1["travisFAILEDssmerge"]
	,fnassscenarios1["Percentual"] + fnassscenarios2["Percentual"])#joining differents types of fn

fnastscenarios1 <- getdata("projectName","numberOfScenarios","travisFAILEDjdimeNoCLWS")
fnastscenarios2 <- getdata("projectName","numberOfScenarios","travisERROREDjdimeNoCLWS")
fnastscenarios <- data.frame(fnastscenarios1["projectName"]
	,fnastscenarios1["numberOfScenarios"]
	,fnastscenarios2["travisERROREDjdimeNoCLWS"]
	,fnastscenarios1["travisFAILEDjdimeNoCLWS"]
	,fnastscenarios1["Percentual"] + fnastscenarios2["Percentual"])#joining differents types of fn


#false negatives by chance of conflict in methods
fnassscenarios1 <- getdata("projectName","scenariosWithCommonChangedMethods","travisFAILEDssmerge")
fnassscenarios2 <- getdata("projectName","scenariosWithCommonChangedMethods","travisERROREDssmerge")
fnassscenariosByConfChancMethods <- data.frame(fnassscenarios1["projectName"]
	,fnassscenarios1["scenariosWithCommonChangedMethods"]
	,fnassscenarios2["travisERROREDssmerge"]
	,fnassscenarios1["travisFAILEDssmerge"]
	,fnassscenarios1["Percentual"] + fnassscenarios2["Percentual"])#joining differents types of fn
fnassscenariosByConfChancMethodsNoZero <- filterZeroDataFPFN(fnassscenariosByConfChancMethods)


fnastscenarios1 <- getdata("projectName","scenariosWithCommonChangedMethods","travisFAILEDjdimeNoCLWS")
fnastscenarios2 <- getdata("projectName","scenariosWithCommonChangedMethods","travisERROREDjdimeNoCLWS")
fnastscenariosByConfChancMethods <- data.frame(fnastscenarios1["projectName"]
	,fnastscenarios1["scenariosWithCommonChangedMethods"]
	,fnastscenarios2["travisERROREDjdimeNoCLWS"]
	,fnastscenarios1["travisFAILEDjdimeNoCLWS"]
	,fnastscenarios1["Percentual"] + fnastscenarios2["Percentual"])#joining differents types of fn
fnastscenariosByConfChancMethodsNoZero <- filterZeroDataFPFN(fnastscenariosByConfChancMethods)
```
   
## Which strategy reports fewer false positives? {.tabset .tabset-fade .tabset-pills}

### Semistructured Merge Additional False Positives

#### By All Scenarios

On average **`r fpassscenarios[fpassscenarios$projectName == "MEAN",][,4]`%** of the considered merge scenarios, had semistructured merge additional falses positives, with a standard deviation of **`r fpassscenarios[fpassscenarios$projectName == "STANDARD DEVIATION",][,4]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r fpassscenarios[fpassscenarios$projectName == "TOTAL",][,4]`%**  of the considered merge scenarios.


```{r}
  datatable(fpassscenarios, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Merge Scenarios', 'Merge Scenarios with Semistructured Merge Additional False Positives *','%'),caption = htmltools::tags$caption( style = 'caption-side: bottom;','* Successful TRAVIS\' builds')) 
```

#### When there is chance of conflicts in Methods

On average **`r fpassscenariosByConfChancMethods[fpassscenariosByConfChancMethods$projectName == "MEAN",][,4]`%** of the considered merge scenarios, had semistructured merge additional falses positives, with a standard deviation of **`r fpassscenariosByConfChancMethods[fpassscenariosByConfChancMethods$projectName == "STANDARD DEVIATION",][,4]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r fpassscenariosByConfChancMethods[fpassscenariosByConfChancMethods$projectName == "TOTAL",][,4]`%**  of the considered merge scenarios.
<!-- (`r round(mean(fpassscenariosByConfChancMethodsNoZero$Percentual,na.rm=TRUE),2)` ± `r round(sd(fpassscenariosByConfChancMethodsNoZero$Percentual,na.rm=TRUE),2)`% filtering zero-occurrences)-->

```{r}
  datatable(fpassscenariosByConfChancMethods, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Merge Scenarios', 'Merge Scenarios with Semistructured Merge Additional False Positives *','%'),caption = htmltools::tags$caption( style = 'caption-side: bottom;','* Successful TRAVIS\' builds')) 
```

### Structured Merge Additional False Positives

#### By All Scenarios

On average **`r fpastscenarios[fpastscenarios$projectName == "MEAN",][,4]`%** of the considered merge scenarios, had structured merge additional falses positives, with a standard deviation of **`r fpastscenarios[fpastscenarios$projectName == "STANDARD DEVIATION",][,4]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r fpastscenarios[fpastscenarios$projectName == "TOTAL",][,4]`%**  of the considered merge scenarios.

```{r}
  datatable(fpastscenarios, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Merge Scenarios', 'Merge Scenarios with Structured Merge Additional False Positives *','%'),caption = htmltools::tags$caption( style = 'caption-side: bottom;','* Successful TRAVIS\' builds.')) 
```

#### When there is chance of conflicts in Methods

On average **`r fpastscenariosByConfChancMethods[fpastscenariosByConfChancMethods$projectName == "MEAN",][,4]`%** of the considered merge scenarios, had structured merge additional falses positives, with a standard deviation of **`r fpastscenariosByConfChancMethods[fpastscenariosByConfChancMethods$projectName == "STANDARD DEVIATION",][,4]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r fpastscenariosByConfChancMethods[fpastscenariosByConfChancMethods$projectName == "TOTAL",][,4]`%**  of the considered merge scenarios.
<!-- (`r round(mean(fpastscenariosByConfChancMethodsNoZero$Percentual,na.rm=TRUE),2)` ± `r round(sd(fpastscenariosByConfChancMethodsNoZero$Percentual,na.rm=TRUE),2)`% filtering zero-occurrences)-->


```{r}
  datatable(fpastscenariosByConfChancMethods, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Merge Scenarios', 'Merge Scenarios with Structured Merge Additional False Positives *','%'),caption = htmltools::tags$caption( style = 'caption-side: bottom;','* Successful TRAVIS\' builds.')) 
```

##
Statistical significance, consider a confidence level of 0.95 (p-value = 0.05):

```{r}
	aux <- head(fpastscenariosByConfChancMethods, -3)
	aFP_ST  = subset(aux, select = c("Percentual"))
	aFP_ST  <- setNames(aFP_ST, c("Structured"))
	
	aux <- head(fpassscenariosByConfChancMethods, -3)
	aFP_SS  = subset(aux, select = c("Percentual"))
	aFP_SS  <- setNames(aFP_SS, c("Semistructured"))
	print(wilcox.test(aFP_ST$Structured,aFP_SS$Semistructured,paired=TRUE))
```

Strength/magnitude of the statistical claim (_effect size_):
 
```{r}
	print(cliff.delta(aFP_ST$Structured,aFP_SS$Semistructured,return.dm=TRUE))
```
 


## Which strategy has fewer false negatives? {.tabset .tabset-fade .tabset-pills}

### Semistructured Merge Additional False Negatives

#### By All Scenarios

On average **`r fnassscenarios[fnassscenarios$projectName == "MEAN",][,5]`%** of the considered merge scenarios, had semistructured merge additional falses negatives, with a standard deviation of **`r fnassscenarios[fnassscenarios$projectName == "STANDARD DEVIATION",][,5]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r fnassscenarios[fnassscenarios$projectName == "TOTAL",][,5]`%**  of the considered merge scenarios.

```{r}
  datatable(fnassscenarios, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Merge Scenarios', 'Semistructured Merge Scenarios with Compilation Issues *','Semistructured Merge Scenarios with Failed Tests *','%'),caption = htmltools::tags$caption( style = 'caption-side: bottom;','* Errored and Failed TRAVIS\' builds,  respectively.'))  
```

#### When there is chance of conflicts in Methods

On average **`r fnassscenariosByConfChancMethods[fnassscenariosByConfChancMethods$projectName == "MEAN",][,5]`%** of the considered merge scenarios, had semistructured merge additional falses negatives, with a standard deviation of **`r fnassscenariosByConfChancMethods[fnassscenariosByConfChancMethods$projectName == "STANDARD DEVIATION",][,5]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r fnassscenariosByConfChancMethods[fnassscenariosByConfChancMethods$projectName == "TOTAL",][,5]`%**  of the considered merge scenarios.
<!-- (`r round(mean(fnassscenariosByConfChancMethodsNoZero$Percentual,na.rm=TRUE),2)` ± `r round(sd(fnassscenariosByConfChancMethodsNoZero$Percentual,na.rm=TRUE),2)`% filtering zero-occurrences)-->


```{r}
  datatable(fnassscenariosByConfChancMethods, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Merge Scenarios', 'Semistructured Merge Scenarios with Compilation Issues *','Semistructured Merge Scenarios with Failed Tests *','%'),caption = htmltools::tags$caption( style = 'caption-side: bottom;','* Errored and Failed TRAVIS\' builds,  respectively.'))  
```

 
### Structured Merge Additional False Negatives

#### By All Scenarios

On average **`r fnastscenarios[fnastscenarios$projectName == "MEAN",][,5]`%** of the considered merge scenarios, had structured merge additional falses negatives, with a standard deviation of **`r fnastscenarios[fnastscenarios$projectName == "STANDARD DEVIATION",][,5]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r fnastscenarios[fnastscenarios$projectName == "TOTAL",][,5]`%**  of the considered merge scenarios.

```{r}
  datatable(fnastscenarios, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Merge Scenarios', 'Structured Merge Scenarios with Compilation Issues *','Structured Merge Scenarios with Failed Tests *','%'),caption = htmltools::tags$caption( style = 'caption-side: bottom;','* Errored and Failed TRAVIS\' builds,  respectively.'))  
```

#### When there is chance of conflicts in Methods

On average **`r fnastscenariosByConfChancMethods[fnastscenariosByConfChancMethods$projectName == "MEAN",][,5]`%** of the considered merge scenarios, had structured merge additional falses negatives, with a standard deviation of **`r fnastscenariosByConfChancMethods[fnastscenariosByConfChancMethods$projectName == "STANDARD DEVIATION",][,5]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r fnastscenariosByConfChancMethods[fnastscenariosByConfChancMethods$projectName == "TOTAL",][,5]`%**  of the considered merge scenarios.
<!-- (`r round(mean(fnastscenariosByConfChancMethodsNoZero$Percentual,na.rm=TRUE),2)` ± `r round(sd(fnastscenariosByConfChancMethodsNoZero$Percentual,na.rm=TRUE),2)`% filtering zero-occurrences)-->

```{r}
  datatable(fnastscenariosByConfChancMethods, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Merge Scenarios', 'Structured Merge Scenarios with Compilation Issues *','Structured Merge Scenarios with Failed Tests *','%'),caption = htmltools::tags$caption( style = 'caption-side: bottom;','* Errored and Failed TRAVIS\' builds,  respectively.'))  
```

##
Statistical significance, consider a confidence level of 0.95 (p-value = 0.05):

```{r}
	aux <- head(fnastscenariosByConfChancMethods, -3)
	aFN_ST  = subset(aux, select = c("Percentual"))
	aFN_ST  <- setNames(aFN_ST, c("Structured"))
	
	aux <- head(fnassscenariosByConfChancMethods, -3)
	aFN_SS  = subset(aux, select = c("Percentual"))
	aFN_SS  <- setNames(aFN_SS, c("Semistructured"))
	print(wilcox.test(aFN_ST$Structured,aFN_SS$Semistructured,paired=TRUE))
```

Strength/magnitude of the statistical claim (_effect size_):
 
```{r}
	print(cliff.delta(aFN_ST$Structured,aFN_SS$Semistructured,return.dm=TRUE))
```

#### Summary False Positives and False Negatives
```{r}
aFN_SS = as.numeric(fnassscenarios[fnassscenarios$projectName == "TOTAL",][,3]) + as.numeric(fnassscenarios[fnassscenarios$projectName == "TOTAL",][,4])
aFN_ST = as.numeric(fnastscenarios[fnastscenarios$projectName == "TOTAL",][,3]) + as.numeric(fnastscenarios[fnastscenarios$projectName == "TOTAL",][,4])
aFPFN_summary <- data.frame(" " = c("aFP","aFN"), 
  "ss" = c(
    fpassscenarios[fpassscenarios$projectName == "TOTAL",][,3], 
    aFN_SS
  ), 
  "st" = c(
    fpastscenarios[fpastscenarios$projectName == "TOTAL",][,3],
    aFN_ST
  )
)
datatable(aFPFN_summary, class = 'cell-border stripe compact stripe', colnames = c('', 'Semistructured Merge','Structured Merge'))
```

#### Manual Analysis for Errored and Failing Builds

* See on [Google Docs](https://docs.google.com/spreadsheets/d/1Lil1L3oiYypZxQsFH23v09w0BySsas4PUnaEsyrqnU8/edit#gid=1220466832)



```{r}
	###############################################################
	#DIFFERENCES EXCLUDING CONSECUTIVE LINES AND SPACING CONFLICTS#
	###############################################################
	
	#differences by all scenarios
	conflictingScenariosOnlyWithSsmergeConf <- getdata("projectName","numberOfScenarios","scenariosOnlyWithSsmergeConfNoCLWS")
	conflictingScenariosOnlyWithJdimeConf <- getdata("projectName","numberOfScenarios","scenariosOnlyWithJdimeConfNoCLWS")
	diffByAllScenariosNoCLWS <- data.frame(conflictingScenariosOnlyWithSsmergeConf["projectName"]
		,conflictingScenariosOnlyWithSsmergeConf["numberOfScenarios"]
		,conflictingScenariosOnlyWithSsmergeConf["scenariosOnlyWithSsmergeConfNoCLWS"]
		,conflictingScenariosOnlyWithJdimeConf["scenariosOnlyWithJdimeConfNoCLWS"]
		,conflictingScenariosOnlyWithSsmergeConf["Percentual"] + conflictingScenariosOnlyWithJdimeConf["Percentual"])#joining differents types of fn
	diffByAllScenariosNoCLWSNoZero <- filterZeroData(diffByAllScenariosNoCLWS, "Percentual")

	#differences by conflicting scenarios
	conflictingScenariosOnlyWithSsmergeConf <- getdata("projectName","conflictingScenariosNoCLWS","scenariosOnlyWithSsmergeConfNoCLWS")
	conflictingScenariosOnlyWithJdimeConf <- getdata("projectName","conflictingScenariosNoCLWS","scenariosOnlyWithJdimeConfNoCLWS")
	diffByConflictingScenariosNoCLWS <- data.frame(conflictingScenariosOnlyWithSsmergeConf["projectName"]
		,conflictingScenariosOnlyWithSsmergeConf["conflictingScenariosNoCLWS"]
		,conflictingScenariosOnlyWithSsmergeConf["scenariosOnlyWithSsmergeConfNoCLWS"]
		,conflictingScenariosOnlyWithJdimeConf["scenariosOnlyWithJdimeConfNoCLWS"]
		,conflictingScenariosOnlyWithSsmergeConf["Percentual"] + conflictingScenariosOnlyWithJdimeConf["Percentual"])#joining differents types of fn
	diffByConflictingScenariosNoCLWSNoZero <- filterZeroData(diffByConflictingScenariosNoCLWS, "Percentual")

	#differences by scenarios with chance of conflict in files
	conflictingScenariosOnlyWithSsmergeConf <- getdata("projectName","scenariosWithCommonChangedFiles","scenariosOnlyWithSsmergeConfNoCLWS")
	conflictingScenariosOnlyWithJdimeConf <- getdata("projectName","scenariosWithCommonChangedFiles","scenariosOnlyWithJdimeConfNoCLWS")
	diffByconfChanceFilesNoCLWS <- data.frame(conflictingScenariosOnlyWithSsmergeConf["projectName"]
		,conflictingScenariosOnlyWithSsmergeConf["scenariosWithCommonChangedFiles"]
		,conflictingScenariosOnlyWithSsmergeConf["scenariosOnlyWithSsmergeConfNoCLWS"]
		,conflictingScenariosOnlyWithJdimeConf["scenariosOnlyWithJdimeConfNoCLWS"]
		,conflictingScenariosOnlyWithSsmergeConf["Percentual"] + conflictingScenariosOnlyWithJdimeConf["Percentual"])#joining differents types of fn
	diffByconfChanceFilesNoCLWSNoZero <- filterZeroData(diffByconfChanceFilesNoCLWS, "Percentual")

		
	#differences by scenarios with chance of conflict in methods
	conflictingScenariosOnlyWithSsmergeConf <- getdata("projectName","scenariosWithCommonChangedMethods","scenariosOnlyWithSsmergeConfNoCLWS")
	conflictingScenariosOnlyWithJdimeConf <- getdata("projectName","scenariosWithCommonChangedMethods","scenariosOnlyWithJdimeConfNoCLWS")
	diffByconfChanceMethodsNoCLWS <- data.frame(conflictingScenariosOnlyWithSsmergeConf["projectName"]
		,conflictingScenariosOnlyWithSsmergeConf["scenariosWithCommonChangedMethods"]
		,conflictingScenariosOnlyWithSsmergeConf["scenariosOnlyWithSsmergeConfNoCLWS"]
		,conflictingScenariosOnlyWithJdimeConf["scenariosOnlyWithJdimeConfNoCLWS"]
		,conflictingScenariosOnlyWithSsmergeConf["Percentual"] + conflictingScenariosOnlyWithJdimeConf["Percentual"])#joining differents types of fn
	diffByconfChanceMethodsNoCLWSNoZero <- filterZeroData(diffByconfChanceMethodsNoCLWS, "Percentual")
```

## Does ignoring conflicts caused by changes to consecutive lines make the strategies more similar? 
 
```{r}
  conflictingScenariosSsmerge  <- getdata("projectName","numberOfScenarios","scenariosWithSsmergeConfNoCLWS")
  conflictingScenariosJdime <- getdata("projectName","numberOfScenarios","scenariosWithJdimeConf")
  conflictingScenarios <- data.frame(conflictingScenariosSsmerge["projectName"]
  	,conflictingScenariosSsmerge["numberOfScenarios"]
  	,conflictingScenariosSsmerge["scenariosWithSsmergeConfNoCLWS"]
  	,conflictingScenariosJdime["scenariosWithJdimeConf"]
  )
```

### How many conflicts arise from the use of semistructured and structured merge? (excl. consecutive lines)

```{r}
totalConflicts <- getdata("projectName","ssmergeConfNoCLWS","jdimeConf")
total_SS = as.numeric(totalConflicts[totalConflicts$projectName == "TOTAL",][,2]) 
total_ST = as.numeric(totalConflicts[totalConflicts$projectName == "TOTAL",][,3])
aFPFN_summary <- data.frame("Semistructured Merge" = c(total_SS), "Structured Merge" = c(total_ST))
```

There is a difference of **`r round(((total_ST - total_SS)/total_SS)*100,2)`%** in the number of reported conflicts.

```{r}
datatable(aFPFN_summary, class = 'cell-border stripe compact stripe', colnames = c('Semistructured Merge','Structured Merge'))
```

Merge scenarios had at least one conflict with _semistructured_ merge on average **`r conflictingScenariosSsmerge[conflictingScenariosSsmerge$projectName == "MEAN",][,4]`%** of the considered merge scenarios, with a standard deviation of **`r conflictingScenariosSsmerge[conflictingScenariosSsmerge$projectName == "STANDARD DEVIATION",][,4]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r conflictingScenariosSsmerge[conflictingScenariosSsmerge$projectName == "TOTAL",][,4]`%**  of the considered merge scenarios. Besides that, merge scenarios had at least one conflict with _structured_ merge on average **`r conflictingScenariosJdime[conflictingScenariosJdime$projectName == "MEAN",][,4]`%** of the considered merge scenarios, with a standard deviation of **`r conflictingScenariosJdime[conflictingScenariosJdime$projectName == "STANDARD DEVIATION",][,4]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r conflictingScenariosJdime[conflictingScenariosJdime$projectName == "TOTAL",][,4]`%**  of the considered merge scenarios.


```{r}
  datatable(conflictingScenarios, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Merge Scenarios', 'Conflicting Semistructured Merge Scenarios','Conflicting Structured Merge Scenarios'))  
```

### How often semistructured and structured merge differ with respect to conflict occurrence? (excl. consecutive lines) {.tabset .tabset-fade .tabset-pills}
#### By All Scenarios

The tools differ on average **`r diffByAllScenariosNoCLWS[diffByAllScenariosNoCLWS$projectName == "MEAN",][,5]`%** of the considered merge scenarios, with a standard deviation of **`r diffByAllScenariosNoCLWS[diffByAllScenariosNoCLWS$projectName == "STANDARD DEVIATION",][,5]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r diffByAllScenariosNoCLWS[diffByAllScenariosNoCLWS$projectName == "TOTAL",][,5]`%**  of the considered merge scenarios.
<!--(`r diffByAllScenariosNoCLWSNoZero[diffByAllScenariosNoCLWSNoZero$projectName == "MEAN",][,5]` ± `r diffByAllScenariosNoCLWSNoZero[diffByAllScenariosNoCLWSNoZero$projectName == "STANDARD DEVIATION",][,5]`% filtering zero-occurrences)-->


```{r}
  datatable(diffByAllScenariosNoCLWS, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Merge Scenarios', 'Conflicting Merge Scenarios Only With Semistructured Merge','Conflicting Merge Scenarios Only With Structured Merge','%'))  
```

#### By Conflicting Scenarios

The tools differ on average **`r diffByConflictingScenariosNoCLWS[diffByConflictingScenariosNoCLWS$projectName == "MEAN",][,5]`%** of the considered merge scenarios, with a standard deviation of **`r diffByConflictingScenariosNoCLWS[diffByConflictingScenariosNoCLWS$projectName == "STANDARD DEVIATION",][,5]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r diffByConflictingScenariosNoCLWS[diffByConflictingScenariosNoCLWS$projectName == "TOTAL",][,5]`%**  of the considered merge scenarios.
<!--(`r diffByConflictingScenariosNoCLWSNoZero[diffByConflictingScenariosNoCLWSNoZero$projectName == "MEAN",][,5]` ± `r diffByConflictingScenariosNoCLWSNoZero[diffByConflictingScenariosNoCLWSNoZero$projectName == "STANDARD DEVIATION",][,5]`% filtering zero-occurrences)-->


```{r}
  datatable(diffByConflictingScenariosNoCLWS, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Conflicting Merge Scenarios', 'Conflicting Merge Scenarios Only With Semistructured Merge','Conflicting Merge Scenarios Only With Structured Merge','%')) 
```

#### When there is chance of conflicts in Files

The tools differ on average **`r diffByconfChanceFilesNoCLWS[diffByconfChanceFilesNoCLWS$projectName == "MEAN",][,5]`%** of the considered merge scenarios, with a standard deviation of **`r diffByconfChanceFilesNoCLWS[diffByconfChanceFilesNoCLWS$projectName == "STANDARD DEVIATION",][,5]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r diffByconfChanceFilesNoCLWS[diffByconfChanceFilesNoCLWS$projectName == "TOTAL",][,5]`%**  of the considered merge scenarios.
<!--(`r diffByconfChanceFilesNoCLWSNoZero[diffByconfChanceFilesNoCLWSNoZero$projectName == "MEAN",][,5]` ± `r diffByconfChanceFilesNoCLWSNoZero[diffByconfChanceFilesNoCLWSNoZero$projectName == "STANDARD DEVIATION",][,5]`% filtering zero-occurrences)-->


```{r}
  datatable(diffByconfChanceFilesNoCLWS, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Merge Scenarios With Common Changed Files', 'Conflicting Merge Scenarios Only With Semistructured Merge','Conflicting Merge Scenarios Only With Structured Merge','%')) 
```

<!--#### When there is chance of conflicts in Methods

The tools differ on average **`r diffByconfChanceMethodsNoCLWS[diffByconfChanceMethodsNoCLWS$projectName == "MEAN",][,5]`%** of the considered merge scenarios, with a standard deviation of **`r diffByconfChanceMethodsNoCLWS[diffByconfChanceMethodsNoCLWS$projectName == "STANDARD DEVIATION",][,5]`%** . Considering aggregated numbers of all projects of our sample, this corresponds to **`r diffByconfChanceMethodsNoCLWS[diffByconfChanceMethodsNoCLWS$projectName == "TOTAL",][,5]`%**  of the considered merge scenarios.
<!--(`r diffByconfChanceMethodsNoCLWSNoZero[diffByconfChanceMethodsNoCLWSNoZero$projectName == "MEAN",][,5]` ± `r diffByconfChanceMethodsNoCLWSNoZero[diffByconfChanceMethodsNoCLWSNoZero$projectName == "STANDARD DEVIATION",][,5]`% filtering zero-occurrences)-->


```{r}
  #datatable(diffByconfChanceMethodsNoCLWS, class = 'cell-border stripe compact stripe', colnames = c('Project', 'Merge Scenarios With Common Changed Methods', 'Conflicting Merge Scenarios Only With Semistructured Merge','Conflicting Merge Scenarios Only With Structured Merge','%')) 
```


#### Boxplot
```{r}
	#diffboxfile <- drawplots(diffByAllScenariosNoCLWS, diffByConflictingScenariosNoCLWS, diffByconfChanceFilesNoCLWS, diffByconfChanceMethodsNoCLWS)
	#print(diffboxfile)

	par(mar=c(11,6,1,1))
  boxplot(diffByAllScenariosNoCLWS$Percentual,diffByConflictingScenariosNoCLWS$Percentual, diffByconfChanceFilesNoCLWS$Percentual, names=c("All Scenarios", "Conf. Scenarios","Conf. chance in Files"),las=2, ylab = "(%)")
#boxplot(diffByAllScenariosNoCLWS$Percentual,diffByConflictingScenariosNoCLWS$Percentual, diffByconfChanceFilesNoCLWS$Percentual,diffByconfChanceMethodsNoCLWS$Percentual, names=c("All Scenarios", "Conf. Scenarios","Conf. chance in Files", "Conf. chance in Methods"),las=2, ylab = "(%)")
#boxplot(diffByAllScenariosNoCLWS$Percentual,diffByConflictingScenariosNoCLWSNoZero$Percentual, diffByconfChanceFilesNoCLWSNoZero$Percentual,diffByconfChanceMethodsNoCLWSNoZero$Percentual, names=c("All Scenarios", "Conf. Scenarios","Conf. chance in Files", "Conf. chance in Methods"),las=2, ylab = "(%)")
```


